### 2018-05-10 Main.Rmd
Generate basic assoc and feature graphs.

```{r}
lemma_vertices <- lemma_list %>%
  rename("name"="item")

assoc_links <- assoc_pairs %>%
  filter(link==1) %>%
  select(item, pair, item.definition, pair.definition) %>%
  rename("from"="item", "to"="pair")

g <- graph_from_data_frame(assoc_links, directed=FALSE, vertices=lemma_list) %>% simplify()
print(g, e=TRUE, v=TRUE)
```

>>>>

Build graphs

```{r}
assoc_links <- assoc_pairs %>%
  filter(link==1) %>%
  select(item, pair, item.definition, pair.definition)

feature_links <- feature_pairs %>%
  filter(shared > 0) %>% # arbitrary, what does the # of shared links represent?
  select(item, pair, item.definition, pair.definition)

assoc_graph <- graph_from_data_frame(assoc_links, directed=FALSE, vertices=lemma_list) %>%
  simplify()

feature_graph <- graph_from_data_frame(feature_links, directed=FALSE, vertices=lemma_list) %>%
  simplify()

print(assoc_graph, e=TRUE, v=TRUE)
print(feature_graph, e=TRUE, v=TRUE)
```
